On exponential sums arising from the classical doubling method

### 2025-04-08 main.tex
Torus

Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal tori $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subseteq \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$. Define
\[
    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = \epsilon_{\Tilde{\algebraicGroup{T}}} q^{-nm/2}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}({\det}_{\finiteFieldExtension{m}}t) \psi(\trace_{\finiteFieldExtension{m}}t).
\]
\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$? \elad{$q^{-nm/2}$}}
Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters. The following lemma shows that this is well defined.

>>>>

Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$. Define
\[
    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = \epsilon_{\Tilde{\algebraicGroup{T}}} q^{-nm/2}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}({\det}_{\finiteFieldExtension{m}}t) \psi(\trace_{\finiteFieldExtension{m}}t).
\]
\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$? \elad{$q^{-nm/2}$}}
Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters. The following lemma shows that this is well defined.
